Worflow

### 2017-06-02 R/workflow.Rmd
update clustering code

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
library(SummarizedExperiment)
library(scRNAseq)
library(zinbwave)
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(scone)
library(RColorBrewer)
library(digest)
library(scone)
library(slingshot)
library(rARPACK)
library(clusterExperiment)
set.seed(20)
```

@@

```{r rsec_50}
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
ceObj <- RSEC(t(W), k0s = 4:15, alphas = c(0.1), betas = 0.8,
                      clusterFunction = "hierarchical01", minSizes=1,
                      ncores = NCORES,
					  combineProportion = 0.7,mergeMethod = "locfdr", mergeCutoff = 0.01
                      subsampleArgs = list(resamp.num=100,
                                           clusterFunction="kmeans",
                                           clusterArgs=list(nstart=10)),
                      seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
save(ceObj, file = fn)
}
else{
	load(fn)
}
```

>>>>

```{r options, echo=FALSE, results="hide",message=FALSE, error=FALSE, include=FALSE, autodep=TRUE}
knitr::opts_chunk$set(fig.align="center", cache=TRUE, error=FALSE, message=FALSE, warning=TRUE)
#bioconductor:
library(scRNAseq)
library(scone)
library(clusterExperiment)
#github
library(zinbwave)
library(slingshot)
#CRAN
library(ggplot2)
library(gplots)
library(magrittr)
library(matrixStats)
library(Rtsne)
library(RColorBrewer)
library(digest)
library(rARPACK)
set.seed(20)
```

@@

```{r rsec_50}
fn = '../data/clustExp_W_k50.rda'
metadata$clusterLabels[is.na(metadata$clusterLabels)]<- -2 #symbol for samples missing from original clustering
seObj<-SummarizedExperiment(t(W),colData=metadata)
if(runClus) {
 print(system.time(ceObj <- RSEC(seObj, k0s = 4:15, alphas = c(0.1), betas = 0.8,
                      clusterFunction = "hierarchical01", minSizes=1,
                      ncores = NCORES,
					  combineProportion = 0.7,mergeMethod = "locfdr", mergeCutoff = 0.01
                      subsampleArgs = list(resamp.num=100,
                                           clusterFunction="kmeans",
                                           clusterArgs=list(nstart=10)),
                      seqArgs = list(k.min=3, top.can=5), verbose=TRUE))
save(ceObj, file = fn)
}
else{
	load(fn)
}
```
